State Results

### 2023-06-26 reports/state_figures.Rmd
rename

```{r load-data}

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,County\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)"

    ) )
)

# read state-level results
targets_dir <- here("_targets_6_19")

state_res <- tar_read(state_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(state_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v4, 
             store =targets_dir)
   )
  # )%>%
  #  bind_rows(
  #   tar_read(state_v5, 
  #            store =targets_dir)
  # )%>%
  #  bind_rows(
  #   tar_read(state_v6, 
  #            store =targets_dir)
  # )

@@

```{r,fig.width=11}

@@

by_version %>%
  mutate(in_interval = factor(in_interval, 
                             levels = c("Above Interval",
                                        "In Interval",
                                        "Below Interval"
                                        ))) %>%
   ggplot(aes(x= fct_reorder(vlabel,prop,max), 
             fill = in_interval, y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+ scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2"),
                       breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Proportion Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = "Including All States") +
  theme_c() +
#  viridis::scale_fill_viridis(option="mako", begin=.2, discrete=TRUE) +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  theme(
          plot.subtitle = element_text(size=18, 
                                       face='italic', 
                                       margin=margin(4,0,4,0))) +
  scale_x_discrete(labels = (TeX(labels)))

>>>>

```{r load-data, fig.width=10}

# clear labels for versions
versions <- tibble(
  version = c("v1", "v2", "v3", "v4", "v5", "v6", "v7"),
  vlabel = factor(
    c( "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
    "$\\beta$ Centered at Emp. Value",
    "$P(S_1|untested)$ Centered at Emp. Value",
    "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ),
    levels = c(
        "$Priors\\,Do\\,Not\\,Vary\\,by\\,State\\,and\\,Date$", 
        "$\\beta$ Centered at Emp. Value",
         "$P(S_1|untested)$ Centered at Emp. Value",
        "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values",
        "$\\beta$ Centered at Emp. Value (Spline Smoothed)",
         "$P(S_1|untested)$ and $\\beta$ Centered at Emp. Values ($\\beta$ Spline Smoothed)",
        "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$"
    ) )
)

# read state-level results
targets_dir <- here("_targets")

state_res <- tar_read(state_v1, 
                   store =targets_dir) %>% 
  mutate(version = "v1") %>%
  bind_rows(
    tar_read(state_v2,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v3, 
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v4, 
             store =targets_dir)
   )%>%
   bind_rows(
    tar_read(state_v5,
             store =targets_dir)
  )%>%
   bind_rows(
    tar_read(state_v6,
             store =targets_dir)
  ) %>%
   bind_rows(
    tar_read(state_v7,
             store =targets_dir)
  )

@@

```{r,fig.width=14}

@@

by_version %>%
  mutate(in_interval = factor(in_interval, 
                             levels = c("Above Interval",
                                        "In Interval",
                                        "Below Interval"
                                        ))) %>%
   ggplot(aes(x= fct_reorder(vlabel,prop,max), 
             fill = in_interval, y =prop)) + 
  geom_bar(stat="identity",position="stack") +
  theme_c() +
  coord_flip()+ scale_fill_manual(values=c("In Interval" = "#79D2AF",
                             "Above Interval" = "#D2AF79",
                      "Below Interval"="#7997D2"),
                       breaks = c("Below Interval",
                               "In Interval",
                               "Above Interval")) +
  labs(x="", 
       y= "Proportion",
       fill = "Covidestim Median:",
       title = "Proportion of Simulation Intervals Where Covidestim Median\nWas Within, Above, or Below the Median",
       subtitle = "Including All States") +
  theme_c() +
  theme_c(legend.position="right",
          legend.title = element_text(face="bold", size = 15),
          legend.text= element_text( size = 15),
          legend.spacing.y = unit(3, 'pt'),
          axis.text.y = element_text(size = 17, hjust=1)) +
  theme(plot.title = element_text(size = 20),
          plot.subtitle = element_text(size=18, 
                                       face='italic', 
                                       margin=margin(4,0,4,0)),
        axis.text.x=element_text(size=12),
        axis.title = element_text(size=14)) +
  scale_x_discrete(labels = (TeX(labels)))

# Simulation Intervals

```{r}

subset <- state_res %>%
  filter(vlabel ==  "$\\,$CTIS Priors that Do Not Vary by State or Date$\\,$")
